---
title: "W8 Examples 1"
author: "Till Krenz"
date: "12/4/2019"
output:
  pdf_document: default
  html_document: default
bibliography: MyCollection.bib
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	dev.args = list(type = "cairo")
)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


```{r load data}
data(mtcars)
```


We can include R code inline as well like this: The average amount of cylinders of the cars in the mtcars dataset is `r mean(mtcars$cyl)`.

## Nice Tables

Now let's create some better looking tables. The following looks good in RStudio, but after rendering not that much.

```{r cars}
head(mtcars)
```

knitr::kable() creates an actual table in the target format (In RStudio it doesn't lool that nice though!)

```{r}
library(knitr)

kable(head(mtcars))
```

The kableExtra package allows us to manipulate the output tables in detail:

```{r}
library(kableExtra)

kable(head(mtcars)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  row_spec(0, angle = -45)
```

```{r}
mtcars %>% 
  count(cyl) %>% 
  mutate(percent = n / sum(n) * 100) %>% 
  kable()
```




