---
title: "W8 Examples 4"
author: "Till Krenz"
date: "12/4/2019"
always_allow_html: yes
bibliography: MyCollection.bib
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	dev.args = list(type = "cairo")
)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


```{r load data}
data(mtcars)
```


We can include R code inline as well like this: The average amount of cylinders of the cars in the mtcars dataset is `r mean(mtcars$cyl)`.

## Nice Tables

Now let's create some better looking tables. The following looks good in RStudio, but after rendering not that much.

```{r cars}
head(mtcars)
```

knitr::kable() creates an actual table in the target format (In RStudio it doesn't lool that nice though!)

```{r}
library(knitr)

kable(head(mtcars))
```

The kableExtra package allows us to manipulate the output tables in detail:

```{r}
library(kableExtra)

kable(head(mtcars)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  row_spec(0, angle = -45)
```

```{r}
mtcars %>% 
  count(cyl) %>% 
  mutate(percent = n / sum(n) * 100) %>% 
  kable()
```



## Regression Tables

```{r}
mod1 <- lm(mpg ~ cyl + vs + gear, data = mtcars)
mod2 <- lm(mpg ~ cyl + vs + gear + hp + disp, data = mtcars)
```


with sjPlot:

```{r}
library(sjPlot)
tab_model(mod1, mod2)
```

with stargazer:

```{r results='asis'}
library(stargazer)
stargazer(mod1, mod2)
```

## Awesome Tables

formattable

```{r}
library(formattable)
formattable(mtcars,
            list(mpg = color_tile("yellow", "orange"),
                 area(col = disp) ~ normalize_bar("pink", 0.2),
                 area(col = hp) ~ normalize_bar("lightgreen", 0.2),
                 vs = formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No")))))
```

reactable

```{r}
library(reactable)

reactable(mtcars)
```

```{r}
reactable(mtcars, filterable = TRUE, searchable = TRUE,
            columns = list(
    mpg = colDef(footer = "mean"),
    cyl = colDef(footer = function(values) mean(values))
  ))
```

## Inserting Citations and a Bibliography

The European languages are members of the same family [@Hsiao2016]. 

As Draz [-@Draz2016, pp. 22-47] shows: their separate existence is a myth.

## Interactive Elements

visNetwork

```{r}
library(visNetwork)
library(igraph)
erdos.renyi.game(22, 0.3) %>% 
visIgraph()
```

htmlwidgets

```{r}
library(ggplot2)
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```


## References
